Software Citation Principles

### 2016-03-10 sc-principles/software-citation-principles.tex
center header in table 2

 & & \multicolumn{7}{c}{Requirements} \\

@@

Author guidelines in F1000Research, APA authors, SSI `publish or be damned' \cite{ssi-publish-or-be-damned} manifesto. \dmnote{There are many other journals publishing software descriptions, some even specialized in software, e.g. \href{http://www.openresearchcomputation.com}{Open Research Computation}.}

>>>>

 & & \multicolumn{9}{c}{Requirements} \\

@@

Author guidelines in F1000Research, APA authors, SSI `publish or be damned'
\cite{ssi-publish-or-be-damned} manifesto, workflow for publishing code using
GitHub and Zenodo \cite{github-citable-code-guide}.
\dmnote{There are many other journals publishing software descriptions, some even specialized in software, e.g. \href{http://www.openresearchcomputation.com}{Open Research Computation}.}
